Reading Notes

### 2020-07-31 2pd.tex
bit by bit

\section*{Motivation}
<why do opvs matter>
In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
<opv performance is intimately linked with structure>
With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
Simulation also helps to give us insight into the atomic interaction which drive self assembly.
A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
The electronic properties are important for light absorption, charge transfer <morehere>
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.

@@

\subsection*{Organic Photovoltaics}
<history>
<how opvs work>
<why morphology matters>
<segue into simulation>

>>>>

\section*{Motivation}
<why do opvs matter>
<energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Maziio2015}
Renewable energy is necessary.
Organic photovoltaics (OPVs) are a potential solution.
<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
OPVs are lightweight, low-cost, and flexible--in order to become the best solution they need better efficiency \cite{Mazzioi2015}.
Currently OPV devices are not efficient enough to solve this problem.
In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
<opv performance is intimately linked with structure>
the interfacial area of the acceptor/donor regions \cite{mazzio} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
Functionalizing a molecule like ITIC can change how it packs in a crystal \cite{Swick2019a}.
By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
Simulation also helps to give us insight into the atomic interaction which drive self assembly.
A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
The electronic properties are important for light absorption, charge transfer \cite{Scharber2006,Hoppe2004,Mazzio2015}
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
<how do we model this system?>

@@

\subsection*{Organic Photovoltaics}
<history>
<how opvs work>
The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can be used to generate excitons.
OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk-heterojunction.
Depending on the bulk morphology of these compounds, the exciton can travel to an accepto-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
<why morphology matters>
<segue into simulation>
